---
title: "Survival analysis guide - WIP"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1) Introduction

-   Introduction to Cox mixed effects model
-   Why do we use it in the lab?

## 2) Script 1 - *requirements.R*

Installation of the required packages should only be done once, or whenever R is updated on your local computer. Be sure to have the most recent source code, available on Github.

### 2.1) Installing packages

    install.packages("dplyr")
    install.packages("coxme")
    install.packages("survminer")
    install.packages("here")

Once the packages have been installed, move on to the second R script.

## 3) Script 2 - *survival-analysis_script.R*

This is the script where the bulk of the analysis takes place. Generally, the script will assume that you are starting in a fresh R session and will initialise the required packages that were installed using the _requirements.R_ script. 

### 3.1) Load installed packages

```
library(dplyr)
library(coxme)
library(survminer)
library(here)
```
The _dplyr_ package allows for efficient data wrangling.

The _coxme_ package is required to run the data through the Cox mixed effects model.

The _survminer_ package is required to build survival curves from the input data. 

The _here_ package allows for efficient file management, across different OS platforms and directories. 




### Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
